Step1_LoadData

### 2024-07-17 ProxySelection.Rmd
preBS

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
```

@@

**Method 9.2: Stepwise Regression (Backward)**
```{r bs, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
stepwise_backward <- stepAIC(full_model, direction = "backward")
fs.backward <- proxy.list[proxy.list %in% fs.backward]
fs.backward <- fs.backward[fs.backward != "exposure"]
proxy.backward <- paste0(fs.backward, collapse = "+")
form.backward <- paste0(c(covform, proxy.backward), collapse = "+")
formula.backward <- as.formula(paste0("exposure", "~", form.backward))

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(autoCovariateSelection)
require(dplyr)
require(cobalt)
require(WeightIt)
library(tidyverse)
library(ggplot2)
library(lmtest)
library(MASS)
library(Boruta)
library(GA)
library(mclust)
library(penalizedSVM)
library(xgboost)
library(caret)
require(autoCovariateSelection)
library(randomForest)
```

@@

**Method 9.2: Stepwise Regression (Backward)**
```{r bs, warning=FALSE, cache=TRUE}
start_time <- Sys.time()
stepwise_backward <- stepAIC(full_model, direction = "backward")
fs.backward <- all.vars(formula(stepwise_backward))[-1]
fs.backward <- proxy.list[proxy.list %in% fs.backward]
fs.backward <- fs.backward[fs.backward != "exposure"]
proxy.backward <- paste0(fs.backward, collapse = "+")
form.backward <- paste0(c(covform, proxy.backward), collapse = "+")
formula.backward <- as.formula(paste0("exposure", "~", form.backward))

@@

```{r rf, warning=FALSE, cache=TRUE}
# Random Forest Feature Selection
start_time <- Sys.time()
rf_model <- randomForest(outcome ~ ., data = hdps.data, importance = TRUE)

# Get important features
rf_importance <- importance(rf_model)
important_features_rf <- rownames(rf_importance)[order(rf_importance[, 1], decreasing = TRUE)]

# Select features
fs_rf <- important_features_rf[important_features_rf %in% proxy.list]
proxy_rf <- paste0(fs_rf, collapse = "+")
form_rf <- paste0(c(covform, proxy_rf), collapse = "+")
formula_rf <- as.formula(paste0("exposure", "~", form_rf))

W.out_rf <- weightit(formula_rf, 
                     data = hdps.data, 
                     estimand = "ATE",
                     method = "ps")

hdps.data$ps_rf <- W.out_rf$ps
hdps.data$w_rf <- W.out_rf$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
fit_rf <- glm(out.formula,
              data = hdps.data,
              weights = W.out_rf$weights,
              family= binomial(link = "logit"))
summary_rf <- summary(fit_rf)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci_rf <- confint(fit_rf, level = 0.95)["exposure", ]
sum_ci_rf <- c(exp(summary_rf[1]), summary_rf, ci_rf)
names(sum_ci_rf) <- c("Odds Ratio",
                      "Estimate",
                      "Std. Error",
                      "Pr(>|z|)",
                      "2.5 %",
                      "97.5 %")

end_time <- Sys.time()
elapsed_time_rf <- as.numeric(difftime(end_time, start_time, units = "secs"))

print("How many proxy variables are in common?")
paste("There are", length(fs_rf), "features selected by randomForest")
paste(length(fs_rf[fs_rf %in% fs.bross]), "of the", length(fs_rf), 
      "are also selected by the bross formula method")

print("The Odds Ratio by Random Forest")
sum_ci_rf
print("Elapsed time for Random Forest:")
elapsed_time_rf
```

```{r rfe, warning=FALSE, cache=TRUE}
# RFE Feature Selection
start_time <- Sys.time()
control <- rfeControl(functions = rfFuncs, method = "cv", number = 10)
results <- rfe(hdps.data[, -which(names(hdps.data) %in% c("outcome", "exposure"))], hdps.data$outcome, sizes = c(1:10), rfeControl = control)

# Get important features
important_features_rfe <- predictors(results)

# Select features
fs_rfe <- important_features_rfe[important_features_rfe %in% proxy.list]
proxy_rfe <- paste0(fs_rfe, collapse = "+")
form_rfe <- paste0(c(covform, proxy_rfe), collapse = "+")
formula_rfe <- as.formula(paste0("exposure", "~", form_rfe))

W.out_rfe <- weightit(formula_rfe, 
                      data = hdps.data, 
                      estimand = "ATE",
                      method = "ps")

hdps.data$ps_rfe <- W.out_rfe$ps
hdps.data$w_rfe <- W.out_rfe$weights
out.formula <- as.formula(paste0("outcome", "~", "exposure"))
fit_rfe <- glm(out.formula,
               data = hdps.data,
               weights = W.out_rfe$weights,
               family= binomial(link = "logit"))
summary_rfe <- summary(fit_rfe)$coef["exposure", c("Estimate", "Std. Error", "Pr(>|z|)")]
ci_rfe <- confint(fit_rfe, level = 0.95)["exposure", ]
sum_ci_rfe <- c(exp(summary_rfe[1]), summary_rfe, ci_rfe)
names(sum_ci_rfe) <- c("Odds Ratio",
                       "Estimate",
                       "Std. Error",
                       "Pr(>|z|)",
                       "2.5 %",
                       "97.5 %")

end_time <- Sys.time()
elapsed_time_rfe <- as.numeric(difftime(end_time, start_time, units = "secs"))

print("How many proxy variables are in common?")
paste("There are", length(fs_rfe), "features selected by RFE")
paste(length(fs_rfe[fs_rfe %in% fs.bross]), "of the", length(fs_rfe), 
      "are also selected by the bross formula method")

print("The Odds Ratio by RFE")
sum_ci_rfe
print("Elapsed time for RFE:")
elapsed_time_rfe
```
